---
title: "Multiple linear regression"
author: "Thomas Willoughby"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(GGally)
library(broom)
```

### Exercise 1

This is an observation study. Given the study design we cannot answer the question posed, as in an observational study one cannot determine causation only correlation.

### Exercise 2

The distribution is left skewed. This indicates that there are few students giving the professors low rating. This is roughly what I would expect to see as there will always be some ratting at the lower end.

```{r}
ggplot(data = evals, aes(x = score)) +
  geom_histogram()
```

### Exercise 3

The maximum beauty average seems to decrease as age increases.

```{r}
ggplot(data = evals, aes(x = age, y = bty_avg)) +
  geom_point()
```

### Exercise 4

```{r}
ggplot(data = evals, aes(x = bty_avg, y = score)) +
  geom_jitter()

ggplot(data = evals, aes(x = bty_avg, y = score)) +
  geom_jitter()
```

### Exercise 5

```{r}
m_bty <- lm(score ~ bty_avg, data = evals)
summary(m_bty)
```

$$
\hat{score} = 0.06664\cdot \text{bty_avg} +3.88034
$$

The slope of 0.06664 indicates that for every increase of one in beauty average score goes up by 0.06664.
