---
title: "Multiple linear regression"
author: "Thomas Willoughby"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(GGally)
library(broom)
```

### Exercise 1

This is an observation study. Given the study design we cannot answer the question posed, as in an observational study one cannot determine causation only correlation.

### Exercise 2

The distribution is left skewed. This indicates that there are few students giving the professors low rating. This is roughly what I would expect to see as there will always be some ratting at the lower end.

```{r}
ggplot(data = evals, aes(x = score)) +
  geom_histogram()
```

### Exercise 3

The maximum beauty average seems to decrease as age increases.

```{r}
ggplot(data = evals, aes(x = age, y = bty_avg)) +
  geom_point()
```

### Exercise 4

```{r}
ggplot(data = evals, aes(x = bty_avg, y = score)) +
  geom_jitter()

ggplot(data = evals, aes(x = bty_avg, y = score)) +
  geom_jitter()
```

### Exercise 5

```{r}
# TODO: ^DO THIS^
m_bty <- lm(score ~ bty_avg, data = evals)
summary(m_bty)
```

$$
\hat{score} = 0.06664\cdot \text{bty_avg} +3.88034
$$

The slope of 0.06664 indicates that for every increase of one in beauty average score goes up by 0.06664. Yes, the average beauty score is statisticaly significant predictor for score. However It is not a practicaly significant predictor.

### Exercise 6

```{r}
evals_aug1 <- augment(m_bty)

evals_aug1 %>% ggplot(aes(x = .resid)) +
  geom_histogram()
```

The distribution of residuals does not approximately normal.

```{r}
evals_aug1 %>% ggplot(aes(x = .fitted, y = .resid)) +
  geom_point()
```

The scatterplot does not show any patterns.

### Exercise 7

```{r}
m_bty_gen <- lm(score ~ bty_avg + gender, data = evals)
tidy(m_bty_gen)


evals_aug2 <- augment(m_bty_gen)

evals_aug2 %>% ggplot(aes(x = .resid)) +
  geom_histogram()

evals_aug2 %>% ggplot(aes(x = .fitted, y = .resid)) +
  geom_point()

```
